\normalfont \normalsize \textsc{UNSW School of Computer Science and Engineering} \\ [24pt] \horrule{1pt} \\[0.5cm] \LARGE Word Embedding and Question Answering \\ \horrule{1pt} \\[0.5cm]

### 2019-12-11 paper.tex
BERT

\usepackage{hyperref}
\usepackage{graphicx}

@@

\subsection{Embedding from Language Model (ELMo)}
All the above models does not consider words with multiple meanings. Peters published a paper in 2018 of deep contextualized word representation that models complex characteristics of word use and how these uses vary across linguistic context. \\\\
Remarkably, previous models, after training, get constant vectors, while \textbf{ELMo} only gets a pre-trained vector. And the final output will be calculated after fine-tuning. So \textbf{ELMo} changes NLP from static to dynamic! \\\\
Given a sequence of $N$ tokens, $(t_1, t_2, t_3, ... t_N)$, we propose a forward language model that computes the probabilities of the sequence $t_k$ given all the history token $(t_1, t_2, t_3, ... t_k)$. 
\begin{align*}
p(t_1, t_2, t_3, ... t_N) = \prod^N_{k = 1} p(t_k | t_1, t_2, ... ,t_{k-1})
\end{align*}
The forward: \textbf{ELMo} uses LSTM layer to compute output. At the forward direction, for each position $k$, each LSTM layer outputs a context dependent representation $\vec{\mathbf{h}^{L,M}_{k, j}}$
\subsection{Bidirectional Encoder Representation from Transformer (BERT)}

\section{Question Answering}

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\newcommand{\cev}[1]{\reflectbox{\ensuremath{\vec{\reflectbox{\ensuremath{#1}}}}}}

@@

\subsection{Embedding from Language Model (ELMo)}
  \includegraphics[scale=0.7]{ELMo.png}
  \caption{Two-layer Bidirectional LSTM Backbone}
All the above models does not consider words with multiple meanings. Peters published a paper in 2018 of deep contextualized word representation that models complex characteristics of word use and how these uses vary across linguistic context. \\\\
Remarkably, previous models, after training, get constant vectors, while \textbf{ELMo} only gets a pre-trained vector. And the final output will be calculated after fine-tuning. So \textbf{ELMo} changes NLP from static to dynamic! \\\\
Given a sequence of $N$ tokens, $(t_1, t_2, t_3, ... t_N)$, we propose a forward language model that computes the probabilities of the sequence $t_k$ given all the history token $(t_1, t_2, t_3, ... t_k)$. 
p(t_1, t_2, t_3, ... t_N) = \prod^N_{k = 1} p(t_k | t_1, t_2, ... ,t_{k-1})
The forward: \textbf{ELMo} uses LSTM layer to compute output. At the forward direction, for each position $k$, each LSTM layer outputs a context dependent representation $\vec{\mathbf{h}}^{L,M}_{k, j}$ where $j = 1, 2, 3, ..., L$. The top layer LSTM output $\vec{\mathbf{h}}^{L,M}_{k, j}$ is used to predict the next token $t_{k+1}$ with softmax. \\\\
The backward:  A backward LM is similar to a forward LM, except it runs over the sequence in reverse, predicting the previous token given the future context:
p(t_1, t_2, t_3, ... t_N) = \prod^N_{k = 1} p(t_k | t_{k+1}, t_{k+2}, ... ,t_N)
Its implementation is also quite similar: we produce $\cev{\mathbf{h}}^{L, M}_{k, j}$ of $t_k$ given $(t_{k+1}, t_{k+2}, ... ,t_N)$\\\\
The formulation of \textbf{ELMo} jointly combines the forward and backward directions that maximize the log likelihood: 
\sum^N_{k=1} (logp (t_k | t_1, t_2, ..., t_{k-1}; \theta_x, \vec{\theta}_{LSTM}, \theta_{S}) + 
(logp (t_k | (t_{k+1}, t_{k+2}, ... ,t_N; \theta_x, \cev{\theta}_{LSTM}, \theta_{S})
Hence, for each token $t_k$, \textbf{ELMo} computes a set of $2L+1$ representations. 
& R_k = \{x^{LM}_k, \vec{\mathbf{h}}^{L,M}_{k, j}, \cev{\mathbf{h}}^{L, M}_{k, j} | j = 1, ... L\} \\
& = \{ \mathbf{h}^{L, M}_{k, j} | j = 1, ... L\}
where $\mathbf{h}^{L, M}_{k, j} $ is the token layer. \\\\
More generally, we compute a task specific weighting of all biLM layers:
ELMo^{task}_k = E(R_k ; \theta^{task} = \gamma^{task} \sum^{L}_{j=0} s^{task}_j \mathbf{h}^{L, M}_{k, j} 
where $s^{task}$ is a softmax-nomalized weights and the $\gamma$ allows task to scale the entire \textbf{ELMo} vector. The indices k and j correspond to the index of the word and the index of the layer from which the hidden state is being extracted from.\\\\
  \includegraphics[scale=0.7]{elmoprocee.png}
  \caption{Overview of the procedure on training ELMo}
To summarize:
$\bullet$ \textbf{ELMo} dynamically determines word embedding in downstream task \\\\
$\bullet$ ELMo generates three embeddings: \\
1. word embedding \\
2. 1st LSTM layer embedding \\
3. 2nd LSTM layer embedding \\
$\bullet$ the pre-training step involves getting three embedding $(v_1, v_2, v_3)$ per word. \\\\
$\bullet$ the fine-tuning step involves freezing the embedding and train weight $(w_1, w_2, w_3)$ for $(v_1, v_2, v_3)$ per word. \\\\
$\bullet$ The final embedding is $w_1 v_1 + w_2 v_2 + w_3 v_3$\\\\
Why three embeddings only? because normal words have less or equal to three meanings, and this is practically proven to work the best. 
  \includegraphics[scale=0.7]{elmofunction.png}
  \caption{A graphic elaboration on ELMo function}
\subsection{Bidirectional Encoder Representation from Transformer (BERT)}
\textbf{BERT} is a model published by Google in 2018 Nov that basically takes advantage of all the previous models that we introduced. \\\\
Similar to \textbf{ELMo}, it has two phases: pre-training and fine-tuning, and it also utilizes two-layer bidirectional model. \\\\
Similar to \textbf{Word2Vec}, it also predicts word from a given context, and transform it to a vector.\\\\
It uses Transformer which is a model proposed in the famous paper \textit{Attention is All You Need} instead of RNN-GPT (Generative Pre-training).\\\\

\subsubsection{Transformer}
\subsubsection{Masked Language Model}
 \begin{figure}
  \includegraphics[scale=0.53]{bertinput.png}
  \caption{BERT input representation. The input embeddings are the sum of the token embeddings, the segmentation embeddings and the position embeddings.}
  \label{fig:skip-gram}
\end{figure}
\section{Question Answering}
